Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics

### 2020-01-13 paper/paper.Rmd
draft generating lineups section

<!-- Spatially dependent data sets were simulated using the variogram model on the centroids of each geographic unit. Twelve simulations from the variogram model were created for each of the twelve lineups.

The underlying spatial correlation model was created to provide spatial autocorrelation between neighboring areas using the longitude and latitude values for the Statistical Areas.

$$z = 1$$
$$locations = longitude + latitude$$
-->

@@

XXX Fill in this structure - see commented text

<!-- Discuss simulating the trend data -->

@@

<!-- Scaling data within a lineup -->

@@

Spatially dependent data sets were simulated using the variogram model on the centroids of each geographic unit. Twelve simulations from the variogram model were created for each of the twelve lineups.

A random location was selected for each set of lineup data.
In this location, a trend model was overlaid on the null set of spatially correlated data.
Each set of lineup data was used to produce a choropleth maps and hexagon tile maps. These matched pairs were split between Group A and Group B.

For each lineup these statistics were calculated:

 - accuracy: the proportion of subjects who detected the data plot
 - efficiency: average time taken to respond

>>>>

@@

<!-- Discuss simulating the trend data -->
One map display in each lineup showed a real trend model. 
To created this real data display different methods were applied for each trend type.

The North West to Soth East (NW-SE) distribution was based on the centroid longitude and latitude values, for each of the each geographic units. First, the difference was found between the minimum latitude and longitude of all centroids, and the values of all other centroids in the set of SA3 geographic units.
Using this difference the following formula was applied: $ (-2*latitude) + longitude $.

The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia. For each geographic unit, the distance to the closest capital city can be found when creating the hexagon tile map using the sugarbag [@sugarbag] package.
There are large geographic differences between the centroids of inner-city areas and the rural outback areas. 
To find the geographic units closest to the capital cities, the distance to the closest capital city was rescaled to the power of 8.
The distances were then scaled between 0 and 1, where very small distance from the capital city were near 0, and the farthest centroid from any capital city was allocated the value of 1. The inner-city geographic units were considered those with a scaled distance of less than 0.85.

A similar process was applied to the three cities' trend model. First a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
Only the three sample cities needed to have larger values in the trend model.

The twelve sets of data were split into three trend model groups, four per group.

@@

<!-- Scaling data within a lineup -->
This resulted in the smallest values of the trend model (blue) occurring in Western Australia, the North West of Australia, and the largest values of the trend model (red) occurring in the South East. This resulted in Tasmania being colored completely red.
For the Three cities lineups, scaling was applied separately to the random values simulated for geographic units that were closest to the cities that were not included in the sample.
This ensured that the minimum simulated value for every map had a dark blue color, and the maximum value was colored red. However, the geographic units that were close to the three cities selected were scaled to a larger maximum value so that their greatest values would appear red.

@@

A random location was selected for each set of lineup data.
In this location, the trend model for each lineup was overlaid on the null set of spatially correlated data.
Each set of lineup data was used to produce a choropleth maps and hexagon tile maps. These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.

### 2020-01-13 paper/paper.tex
draft generating lineups section

XXX Fill in this structure - see commented text

@@

Spatially dependent data sets were simulated using the variogram model on the centroids of each geographic unit. Twelve simulations from the variogram model were created for each of the twelve lineups.

@@

A random location was selected for each set of lineup data.
In this location, a trend model was overlaid on the null set of spatially correlated data.
Each set of lineup data was used to produce a choropleth maps and hexagon tile maps. These matched pairs were split between Group A and Group B.

For each lineup these statistics were calculated:

\begin{itemize}
\tightlist
\item
  accuracy: the proportion of subjects who detected the data plot
\item
  efficiency: average time taken to respond
\end{itemize}

@@

\hypertarget{references}{%
\section{References}\label{references}}

>>>>

One map display in each lineup showed a real trend model.
To created this real data display different methods were applied for each trend type.

The North West to Soth East (NW-SE) distribution was based on the centroid longitude and latitude values, for each of the each geographic units. First, the difference was found between the minimum latitude and longitude of all centroids, and the values of all other centroids in the set of SA3 geographic units.
Using this difference the following formula was applied: \$ (-2*latitude) + longitude \$.

The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia. For each geographic unit, the distance to the closest capital city can be found when creating the hexagon tile map using the sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]} package.
There are large geographic differences between the centroids of inner-city areas and the rural outback areas.
To find the geographic units closest to the capital cities, the distance to the closest capital city was rescaled to the power of 8.
The distances were then scaled between 0 and 1, where very small distance from the capital city were near 0, and the farthest centroid from any capital city was allocated the value of 1. The inner-city geographic units were considered those with a scaled distance of less than 0.85.

A similar process was applied to the three cities' trend model. First a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
Only the three sample cities needed to have larger values in the trend model.

The twelve sets of data were split into three trend model groups, four per group.

@@

@@

This resulted in the smallest values of the trend model (blue) occurring in Western Australia, the North West of Australia, and the largest values of the trend model (red) occurring in the South East. This resulted in Tasmania being colored completely red.
For the Three cities lineups, scaling was applied separately to the random values simulated for geographic units that were closest to the cities that were not included in the sample.
This ensured that the minimum simulated value for every map had a dark blue color, and the maximum value was colored red. However, the geographic units that were close to the three cities selected were scaled to a larger maximum value so that their greatest values would appear red.

A random location was selected for each set of lineup data.
In this location, the trend model for each lineup was overlaid on the null set of spatially correlated data.
Each set of lineup data was used to produce a choropleth maps and hexagon tile maps. These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}
